---
title: "An illustrative example for R package `RDRwate`"
author: "Yi Liu"
date: "July 31, 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Load packages and dataset

Uncomment and run the following code for installing the latest version of our package, if you don't have it on your R. 

```{r}
# if (!require("devtools"))
# install.packages("devtools")
# devtools::install_github("yiliu1998/Rate-DR-WATE")
```

Load our package: 

```{r}
library(RDRwate)
```

The following packages are also required in this demonstration: 

```{r}
library(dplyr)
library(SuperLearner)
library(glmnet)
library(caret)
```

Running the following code, two sets of pre-generated observational data (`df.homo` and `df.hete`) will show up in the R environment. 

```{r}
load(system.file("data", "example.Rdata", package="RDRwate"))
```

A quick look to the generated data:

```{r}
head(df.hete)
```

We allow users to specify different methods for nuisance function estimation and prediction in our RDR estimators of WATE. The complete list of these methods can be found using the following code. 

```{r}
SuperLearner::listWrappers()
```

## Data analysis

Next, we can implement our package using code as follows. We consider evaluating the following estimands: ATE (overall), ATT (treated), ATC (controls), ATO (overlap weights), ATM (matching weights), ATEN (entropy), and two ATB's (beta weights, with $\nu_1=\nu_2\in\{3,5\}$). 

As an example, we consider applying our method on the dataset `df.hete`. We include `SL.glm`, `SL.glm.interaction` and `SL.glmnet` in the ensemble library of `SuperLearner` for getting our nuisance function estimates. 

As an important remark, we do not currently allow **missing data** (in all covariates, treatment and outcome) in the dataset. Therefore, if your data have missing values, we suggest either doing a complete-case analysis or imputing missing data first. Once the data is cleaned and prepared, it is ready to run our methods. The first step is to extract the binary treatment vector, outcome vector and covariates matrix (can also be a data frame). 

```{r}
A <- df.hete$A
Y <- df.hete$Y
X <- df.hete %>% select(-A, -Y)
```

Then, plug-in these arguments to our main function `RDRwate()`: 

```{r}
v1 <- c(3,5)
v2 <- c(3,5)
beta=TRUE
result.eif <- RDRwate(A=A, Y=Y, X=X, beta=beta, v1=v1, v2=v2,
                      method="EIF", 
                      ps.library=c("SL.glm", "SL.glmnet"),
                      out.library=c("SL.glm", "SL.glmnet"),
                      seed=1)
print(result.eif)
```

We apply the DML-based methods using 10 sample splits (i.e., repeating cross-fitting 5 times by different random sample splitting) and 5 folds for cross-fitting. 

```{r}
v1 <- c(3,5)
v2 <- c(3,5)
beta=TRUE
result.dml <- RDRwate(A=A, Y=Y, X=X, beta=beta, v1=v1, v2=v2,
                      method="DML", n.folds=5, n.split=10, 
                      ps.library=c("SL.glm", "SL.glmnet"),
                      out.library=c("SL.glm", "SL.glmnet"),
                      seed=1)
print(result.dml)
```

