---
title: "An illustrative example for R package `RDRwate`"
author: "Yi Liu"
date: "July 14, 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Load packages and dataset

Uncomment and run the following code for installing the latest version of our package, if you don't have it on your R. 

```{r}
# if (!require("devtools"))
# install.packages("devtools")
# devtools::install_github("yiliu1998/Rate-DR-WATE")
```

Load our package: 

```{r}
library(RDRwate)
```

The following packages are also required:

```{r}
library(dplyr)
library(ggplot2)
library(SuperLearner)
library(glmnet)
library(caret)
```

Using the following code, we can get two sets of data: `df.hete` and `df.homo`. Both data contain 8 covariates (`X1`--`X8`), a treatment variable (`A`) and an outcome variable (`Y`). The true treatment effect in the `df.hete` (resp. `df.homo`) data is heterogeneous (resp. homogeneous) for individuals. The true average treatment effect (ATE) in both data is generated as 10. 

```{r}
load(system.file("data", "example.Rdata", package="RDRwate"))
```

## Data analysis

We allow users to specify different methods for nuisance function estimation and prediction in our RDR estimators of WATE. The complete list of 

```{r}
SuperLearner::listWrappers()
```

We consider evaluating the following estimands using our package: ATE (overall), ATT (treated), ATC (controls), ATO (overlap weights), ATM (matching weights), ATEN (entropy), and two ATB's (beta weights, with $\nu_1=\nu_2\in\{3,5\}$). 

As an example, we consider applying our method on the dataset `df.hete`. We include `SL.glm`, `SL.glm.interaction` and `SL.glmnet` in the ensemble library of `SuperLearner` for running our methods. 

As an important remark, we do not currently allow missing data (in all covariates, treatment and outcome) in the dataset. Therefore, if your data have missing values, we suggest either a complete-case analysis or imputing missing data first. 

Once the data is cleaned and prepared, it is ready to run our methods. The first step is to extract the binary treatment vector, outcome vector and covariates matrix (can also be a data frame). 

```{r}
A <- df.hete$A
Y <- df.hete$Y
X <- df.hete %>% select(-A, -Y)
```

Then, plug-in these arguments to our main function `RDRwate()`: 

```{r}
v1 <- c(3,5)
v2 <- c(3,5)
result.eif <- RDRwate(A=A, Y=Y, X=X, beta=beta, v1=v1, v2=v2,
                      method="EIF", 
                      ps.library=c("SL.glm", "SL.glm.interaction", "SL.glmnet"),
                      out.library=c("SL.glm", "SL.glm.interaction", "SL.glmnet"),
                      seed=1)
result.eif
```

```{r}
result.dml <- RDRwate(A=A, Y=Y, X=X, beta=beta, v1=v1, v2=v2,
                      method="DML", n.folds=5,
                      ps.library=c("SL.glm", "SL.glm.interaction", "SL.glmnet"),
                      out.library=c("SL.glm", "SL.glm.interaction", "SL.glmnet"),
                      seed=1)
```

